Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-16 main.Rmd
cache ignored except for smart_harmony - file.exists and dir.exists

```{r harmony-tab, echo=FALSE, cache=TRUE}
harmonies <- smart_meter10 %>% 
  harmony(ugran = "month",
          filter_out = c("hhour", "fortnight"))

@@

>>>>

```{r harmony-tab, echo=FALSE, cache=TRUE}
if(!dir.exists("cache/"))
{
  dir.create("cache")
}
if (!file.exists("cache/smart_harmony.rds")) { 
  harmonies <- smart_meter10 %>% 
  harmony(ugran = "month",
          filter_out = c("hhour", "fortnight"))

@@

  write_rds(smart_harmony, "cache/smart_harmony.rds")
}
smart_harmony <- read_rds("cache/smart_harmony.rds")
